Current State of Knowledge Representation Systems for Robotics

### 2011-12-13 krs-survey.tex
Proof-read and extended the scenario part

In order to illustrate what we consider to be the required features of a
knowledge representation system for robotics, we propose the following
scenario.

While devising a scenario inevitably constraints the breadth of abilities we
examine to the ones actually needed for this specific scenario, we insist on
the fact that our main purpose is to demonstrate on a real case what
representational features are desirable.

@@

Robi and Roba are two service robots. They are considered to be able to freely
move and pick objects, but they are not expected to have the exact same
hardware and softwares architectures, and especially, they are not expected to
have the same knowledge representation system. These robots cooperate with a
human in a kitchen environment.

The main task of the scenario is the joint realization of a brownie, that
starts with the human injunction ``Let's make a brownie for tonight!''.

The scenario is successful if the task is achieved (the brownie is made) and:

@@

We voluntarily do not try to detail the subtasks of the scenario and to define
how they are shared amongst agents. In our analysis we focus on the general,
\textit{a priori} representational needs of the scenario.

A ``first-order'' analysis of this task leads to a first list of categories of
required features:

@@

% Representation of a complex task
The first category can be further refined: to prepare and bake a brownie, the
robot first needs to make sense of the very term \emph{brownie}: what is it?
what is it used for? what is it made of? etc. We call this knowledge
\emph{common-sense knowledge} and the robot must be able not only to represent
it, but also to have some kind of access to it (for instance through a initial
set of facts that are made available at startup, or via access to a Web-based
knowledge base like Wikipedia, etc.)

In conjunction with the representation of the action \emph{make} (and it's
possibly attached common-knowledge), this should lead the robot to build and
represent a \emph{context}: we are in a scenario involving cooking. Actions
related to cooking often take place in the kitchen, cooking requires ingredients, 
utensils and a procedure that may be provided by a recipe, etc.

@@

``cooking requires ingredients that may be provided by a recipe'' hints about a
very common feature available in most knowledge representation systems:
\emph{reasoning}. The robot \emph{infers} that cooking may require a recipe
since a list of ingredients is a pre-requisite of the cooking action, and a
recipe may provided such a list. If we omit the ``may'', this is a typical
example of first-order logic reasoning. Many other reasoning techniques exist
(including probabilistic ones -- ones able to deal with the ``may''), we shall
illustrate some of them further in this scenario.

As mentioned, a recipe often provides a procedure (or a \emph{plan}). The robot
should be able to store this plan in a way that allow later execution.  The
plan is likely to contain \emph{spatio-temporal constraints} (like ``put
the brownie in the oven for 20 min'') that must as well be appropriately
represented.

Moreover, procedures are often \emph{underspecified}: we can expect the recipe
to provide a cooking duration, but we usually do not expect the recipe to tell
us to first open the oven door, and then put the cake into it, since it is
self-evident that the door must first be opened. Such underspecification should
be detectable, representable, and ideally completable by the knowledge
representation system.

Besides representation of space and time, we may have

% Representation feature that enable cooperation
Then, we want our three agents to cooperate. This, in turn, leads to a very
different set of cognitive abilities.

Cooperation in our scenario can intervene at many levels: for instance, an
agent may want to inform another one about the number of eggs that are
necessary for the brownie. It makes sense to help in this way only if the first
agent knows that the recipient agent both needs the information and does not
know it. This in turn requires the robot to be able to model the knowledge of
the other agents: to think \emph{from the perspective} of another agent (this
idea is related to the so-called Theory of Mind~\cite{...}).

Ability to communicate is one important pre-requisite to collaboration.
Communication in general~\cite{Jakobson} requires the addresser and the
addressee to share a common interpretative framework (shared common-sense
knowledge -- or cultural background -- and a shared context). In our scenario,
the agents are working in a kitchen. This element of context does not however
suffice if, for example, an agent asks another agent to ``give {[him]} the
bowl''. Besides the symbol ``bowl'', which physical entity are we actually
talking about? If we want to act on the world, this \emph{grounding} operation
is essential, and may be tightly bound to the underlying knowledge
representation system. Note that grounding usually denotes the {\it top-down}
operation: from the symbol to the percept. It is however commonly bundled with
the converse operation, that retrieve (or create) symbols from perception.

@@

Also central to cooperation are the notions of \emph{joint
intentions} and \emph{joint goals}~\cite{Tomasello2005, Bratman2009}: to help
the human during the cooking session, the robots need to store at least how far
they are into the recipe, what is the next step the human is likely to go for,
how task are currently split between agents, what action is currently
blocking the procedure, etc. This knowledge should let the robot identify the
intentions of other agents and create accordingly joint goals. Hence, a
knowledge representation system aiming at dealing with cooperative behaviours
is likely to have goal management structures taking explicitly into account
other agents' actions and goals.

@@

Last but not least, our scenario assumes implicitly \emph{natural interaction}
between humans and robots (as showed by the casual style of the
order ``Let's make a brownie!''). While natural language processing {\it
per-se} is usually out of the scope of a knowledge representation system, we
may want to be sure these systems successfully interoperate, \ie that the
knowledge representation system provides efficient support to the natural
language processing module (for instance by adopting models and vocabulary that
are both well suited for machine processing and remain as close as possible to
the humans own structures and vocabulary).

@@

This distinction is important in robotics were the robot may have to manipulate
concepts with only partial knowledge on them. For instance, let imagine a robot
that sees a bottle over a table, whose bottom is hidden by another object. The
robot can not prove that the bottle is indeed \emph{on} the table. A knowledge
representation system relying on the closed world assumption would then assume
the bottle is \emph{not} on the table ($\lnot R^{CWA}_{isOn}(bottle, table)$)
whereas with the open world assumption, the proposition $R^{OWA}_{isOn}(bottle,
table)$ would be undecided. Example in table~\ref{table|cwa-owa-example} provides
a simple, concrete example of consequences of the CWA/OWA choice on reasoning.

@@

>>>>

In order to illustrate what we consider to be the required features of a
knowledge representation system for robotics, we introduce in this section a
demonstration scenario.

While devising a scenario inevitably constraints the breadth of abilities we
examine, we insist on the fact that our main purpose here is to ground into a
real case the set of representational features we consider as desirable.  We
will \emph{not} evaluate any of the systems we survey in this article by
judging their applicability to this particular scenario.

@@

Robi and Roba are two service robots. They are considered to be able to freely
move and pick objects, but they are not expected to have the exact same
hardware and softwares architectures, and specially, they are not expected to
have the same knowledge representation system. These robots cooperate with a
human in a kitchen environment.

The main task of the scenario is the joint realization of a brownie, initiated
by the human injunction ``Let's make a brownie for tonight!''.

The scenario is successful if the task is achieved (the brownie is baked) and:

@@

We voluntarily do not detail the subtasks of the scenario, neither we define
how they are shared amongst agents. In our analysis we focus on the general,
\textit{a priori} representational needs of the scenario.

A ``first-order'' analysis of this task leads to a first partition of the
required representation abilities:

@@

% Representation of a complex task
We can further refine these categories: to prepare and bake a brownie, the
robot first needs to make sense of the very term \emph{brownie}: what is it?
what is it used for? what is it made of? etc. We call this knowledge
\emph{common-sense knowledge} and the robot must be able not only to represent
it, but also to have some kind of access to it (for instance through a initial
set of facts that are made available at startup, or via access to a Web-based
knowledge base like Wikipedia, etc.)

Bound to the action \emph{make}, this should lead the robot to build and
represent a \emph{context}: we are in a scenario involving cooking. Actions
related to cooking often take place in the kitchen, cooking requires ingredients, 
utensils and a procedure that may be provided by a recipe, etc.

@@

``cooking requires ingredients that may be provided by a recipe'' hints about a
very common feature available in most knowledge representation systems:
\emph{reasoning}. The robot \emph{infers} that cooking may require a recipe
since a list of ingredients is a pre-requisite of the cooking action, and a
recipe may provide such a list. If we omit the ``may'', this is a typical
example of first-order logic reasoning. Many other reasoning techniques exist
(including probabilistic ones -- ones able to deal with the ``may''), we shall
illustrate some of them later in this scenario.

We mentioned that a recipe often provides a procedure (or a \emph{plan}). The robot
should be able to store this plan in a way that allow later execution.  The
plan is likely to contain \emph{spatio-temporal constraints} (like ``put
the brownie in the oven for 20 min'') that must as well be appropriately
represented.

To make decision, a robot may also want to \emph{predict} the state of the world
after some action (``if I leave the cake 2h in the oven, it will be burned'').
Such ability to project itself in future or, generally speaking, in other
possible state of the world is related to several cognitive ability and
reasoning techniques: \emph{planning}, \emph{representation of possible worlds}
and \emph{non-monotonic reasoning}, in addition to common-sense knowledge and
\emph{physics-based reasoning}.

Procedures are in addition often \emph{underspecified}: we can expect the recipe
to provide a cooking duration, but we usually do not expect the recipe to tell
us to first open the oven door, and then put the cake into it, since it is
self-evident that the door must first be opened to put the cake in the oven.
Such underspecification should be detectable, representable, and ideally
completable by the knowledge representation system\footnote{Note that we do not
assume here the {\it knowledge representation system} to be a single software
component: it may well be the result of the aggregation of several modules
working together}.

% Representation feature that enable cooperation
Then, we want our three agents to cooperate. This, in turn, leads to another
set of cognitive abilities.

Cooperation in our scenario can intervene at many places. For instance, an
agent may want to inform another one about the number of eggs that are
necessary for the brownie. This \emph{helping} behaviour makes sense only if
the first agent knows that the recipient agent both needs the information but
does not know it. This in turn requires the robot to be able to model the
knowledge of the other agents: to think \emph{from the perspective} of another
agent (this idea is related to the so-called Theory of Mind~\cite{...}).

Ability to communicate is one important pre-requisite to collaboration.
Communication in general~\cite{Jakobson} requires the addresser and the
addressee to share a common interpretative framework (shared common-sense
knowledge -- or cultural background -- and a shared context). In our scenario,
the agents are working in a kitchen. This element of context does not however
suffice if, for example, an agent asks another agent to ``give {[him]} the
bowl''. Besides the symbol ``bowl'', which physical entity are we actually
talking about? If we want to act on the world, this so-called \emph{grounding}
operation is essential, and may be tightly bound to the underlying knowledge
representation system. Note that grounding usually denotes the {\it top-down}
operation: from the symbol to the percept. It is however commonly bundled with
the converse operation, that retrieve (or create) symbols from perception.

@@

Also central to cooperation are the notions of \emph{joint
intentions} and \emph{joint goals}~\cite{Tomasello2005, Bratman2009}: to help
the human during the cooking session, the robots need to track how far
they are into the recipe, what is the next step the human is likely to go for,
how task are currently split between agents, what action is currently
blocking the procedure, etc. This knowledge should let the robot identify the
intentions of other agents and create accordingly joint goals. Hence, a
knowledge representation system aiming at dealing with cooperative behaviours
is likely to have goal management structures taking explicitly into account
other agents' actions and goals.

@@

Last but not least, our scenario assumes implicitly \emph{natural interaction}
between humans and robots (as showed by the casual style of the
order ``Let's make a brownie!''). While natural language processing {\it
per-se} is usually out of the scope of a knowledge representation system, we
may want to be sure these systems may successfully interoperate, \ie that the
knowledge representation system provides efficient support to the natural
language processing module (for instance by adopting models and vocabulary that
are both well suited for machine processing and remain as close as possible to
the humans own structures and vocabulary).

@@

This distinction is important in robotics were the robot may have to manipulate
concepts with only partial knowledge on them. For instance, let imagine a robot
that sees a bottle on a table, whose bottom is hidden by another object. The
robot can not prove that the bottle is indeed \emph{on} the table. A knowledge
representation system relying on the closed world assumption would then assume
the bottle is \emph{not} on the table ($\lnot R^{CWA}_{isOn}(bottle, table)$)
whereas with the open world assumption, the proposition $R^{OWA}_{isOn}(bottle,
table)$ would be undecided. Example in table~\ref{table|cwa-owa-example} provides
a simple, concrete example of consequences of the CWA/OWA choice on reasoning.

@@

\subsubsection{Physics-based reasoning}
\label{sect|physics}
